---
title: "Lab 07 - Modelling course evaluations"
author: "Team 1_2"
output: 
  tufte::tufte_html:
    css: ../lab.css
    tufte_variant: "envisioned"
    highlight: pygments
link-citations: yes

---

### Load packages 

```{r load-packages, message=FALSE}
library(tidyverse)
library(tidymodels)
library(patchwork)
```

### Read in data

```{r read-data}
evals<-read.csv("data/evals.csv", row.names=1)
```


### Exercise 1

```{r viz-score}
ggplot(evals, aes(score)) +
  geom_bar()
```

This shows that most students rate their courses fairly well, with the distribution peaking around 4.5.

### Exercise 2

```{r viz-score-bty}

plot_geom_point  <- ggplot(evals, aes(bty_avg, score)) +
  geom_point()

plot_geom_jitter <- ggplot(evals, aes(bty_avg, score)) +
  geom_point() + geom_jitter()

plot_geom_point + plot_geom_jitter
```

In the first plot, all the points are on discrete numbers.

### Exercise 3

```{r fit-score_bty_fit}

score_bty_fit <- linear_reg() %>%
  set_engine("lm") %>%
  fit(score ~ bty_avg, data = evals)
```

```{r tidy-score_bty_fit}

tidy(score_bty_fit)
```

score = 3.88 + 0.07 * bty_avg

### Exercise 4

```{r viz-score_bty_fit}
plot_geom_point  <- ggplot(evals, aes(bty_avg, score),) +
  geom_point()+geom_smooth(method = "lm",se=FALSE,colour="orange")

plot_geom_jitter <- ggplot(evals, aes(bty_avg, score)) +
  geom_point() + geom_jitter()+geom_smooth(method = "lm",se=FALSE,colour="orange")

plot_geom_point + plot_geom_jitter
```

### Exercise 5

The higher the perceived beauty of the lecturer, the higher the students will rate their course.

### Exercise 6
It is meaningful, because all points are around score 4, it is possible to rate their beauty 0.

### Exercise 7

```{r glance-score_bty_fit, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
glance(___)
```

*Add interpretation of R-squared here.*

### Exercise 8

```{r viz-score_bty_fit-diagnostic, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_bty_aug <- augment(score_bty_fit$fit)

ggplot(___)
```

*Add your narrative here.*

### Exercise 9

```{r fit-score_rank_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 10

```{r fit-score_gender_fit}
# fit model

# tidy model output
```

```{r score_gender_intercept, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options
score_gender_intercept <- tidy(score_gender_fit) %>% 
  filter(term == "(Intercept)") %>%
  select(estimate) %>%
  pull()
```

```{r score_gender_slope, echo = FALSE, eval = FALSE}
# remove eval = FALSE from the code chunk options after filling in the blanks
score_gender_slope <- tidy(score_gender_fit) %>% 
  filter(term == "___") %>%
  select(___) %>%
  pull()
```

*Add your narrative here.*

### Exercise 11

```{r fit-score_bty_gender_fit}
# fit model

# tidy model output
```

*Add your narrative here.*

### Exercise 12

```{r glance-score_bty_gender_fit}
# glance model output
```

*Add your narrative here.*

### Exercise 13

*Add your linear model here. Don't worry about math notation, you can use things like score-hat.*

### Exercise 14

*Add your narrative here. One sentence is sufficient.*

### Exercise 15

*Add your narrative here. One sentence is sufficient.*

### Exercise 16

*Add your narrative here. One sentence is sufficient.*

### Exercise 17

*Add your narrative here. One sentence is sufficient.*

### Exercise 18

```{r fit-score_bty_gender_rank_fit}
# fit model

# glance model output
```

*Add your narrative here. One sentence is sufficient.*
